\documentclass[12pt]{article}

% REMOVE THIS
\usepackage[latin, english]{babel}
\usepackage{lipsum}  

%% EDIT THIS: set \rightsidetrue for right side years, 
%\rightsidefalse for left side
\newif\ifrightside
% \rightsidetrue
\rightsidefalse

%% EDIT THIS: to bold all mention of \citationboldauthor
\newcommand{\citationboldauthor}{J. J. Doe}

%% OPTIONAL: change url link color
\usepackage[dvipsnames]{xcolor}
\newcommand{\urllinkcolor}{MidnightBlue}

%% IMPORTANT: load template
\usepackage{AcademicCVTemplate}

%% OPTIONAL: change font
\usepackage{fontspec}
\setmainfont[
  Path = fonts/,
  Numbers=OldStyle,
  BoldFont=LinLibertineRB.ttf,
  ItalicFont=LinLibertineRI.ttf
]{LinLibertineR.ttf}

% \cfoot{Page \thepage\ of \pageref*{LastPage}}
\cfoot{\thepage}

\definecolor{dimgray}{rgb}{0.45, 0.45, 0.45}
\newcommand{\smallitem}[1]{\small\textcolor{dimgray}{#1}}


\begin{document}

\begin{leftsideheader}
% THE HEADER
\begin{flushleft}
    \hfill{\updateinfo} \\
    
    {\huge Dylan Di} \\[5pt]
    % {\centering \huge Jane-John Doe\par}
    
    635 South Hobart Boulevard \hfill \texttt{qdi@usc.edu} \\
    
    Los Angeles, CA 90005, USA \hfill \texttt{(818)688-3330} \\
\end{flushleft}
{\centering\rule{7.4in}{1pt}\par}
% \cvtitle{Curriculum Vitae}
\end{leftsideheader}

\section{Education}
\textsc{University of Southern California, Los Angeles, CA} \years{08/2022 - 05/2024}\\ 
Master of Urban Planning. Concentration: Mobility and Transportation Planning.\\

\textsc{The University of British Columbia, Vancouver, BC} \years{09/2018 - 05/2022}\\
Bachelor of Arts. Majors: Geography. Minor: Urban Studies.\\


\section{Research Experience}
Directed Research. \years{08/2023 - 12/2023}\\
\textsc{USC Sol Price School of Public Policy, Los Angelse, CA}\\
\smallitem{Supervisor: Professor Genevieve Giuliano}\\


Research Assistant. \years{08/2022 - 11/2022}\\
\textsc{USC Sol Price School of Public Policy, Los Angeles, CA} \\
\smallitem{PI: Professor Geoff Boeing}\\


Research Seminar. \years{01/2022 - 04/2022}\\
\textsc{UBC Department of Geography, Vancouver, BC}\\
\smallitem{Instructor: Dr. Natasha Fox}\\



\section{Publications}
\begin{etaremune}[itemsep=0pt, parsep=0pt, leftmargin = \enumleftmargin] 
    \citeitem{https://doi.org/10.1145/3495018.3501157}{Q. Di, L. Yang, M. An}{Research on Spatial Accessibility of Urban Facilities Using Geographic Information Science and Road Network Data}{2021}{2021 3rd International Conference on Artificial Intelligence and Advanced Manufacture}{2650, 2654}
\end{etaremune}


\section{Professional Employment}
Transportation Engineering/Planning Intern. \years{05/2023 - }\\
\textsc{Fehr and Peers, Long Beach, CA}\\

GIS Intern. \years{04/2021 - 08/2021} \\
\textsc{China Northeastern Municipal Engineering Design and Research Institute, Changchun, China} \\

Assistant Project Manager. \years{05/2020 - 10/2020} \\
\textsc{Anhui Zhonghui Jianyin Construction and Management Co., Ltd, Huaibei, China} \\


\section{Service and Volunteering}
International Chair. \years{04/2023 - 04/2024}\\
\textsc{Associated Students of Planning and Development at USC}\\

Staff. \years{02/2023 - 03/2023}\\
\textsc{The sixth annual Region 9 Pacific Southwest Region University Center Congress}\\

\section{Professional Membership}
\textsc{American Planning Association},  \ Los Angeles Chapter\\
\textsc{Ameican Association of Geographers}\\
\textsc{Urban Land Institute}\\
\textsc{Canadian Institue of Planners}\\
\textsc{Canadian Association of Geographers}\\


\section{Technical Skills}
Programming languages: Python, R, SAS

Geographic Information Systems: ArcGIS, QGIS

Traffic Operations: Synchro, PTV Vistro, ITE TripGen

Visualizations: Adobe Creative Cloud\ (Photoshop, Illustrator, InDesign)

Languages: Chinese-Mandarin\ (Native Proficiency), English\ (Full Professional Proficiency), Chinese-Cantonese\ (Limited Working Proficiencye)

\end{document}